### 2021-05-10 papers/SYRCoSE/regmachine-eventstruct.tex
fix: side condition in Load rule
fix: proof of Threorem 1

First, we need to show that $\caOrd \ \defeq \ (\lPO \cup \lRF)^*$
is a partial order. Reflexivity and transitivity follows immediately 
from the definition of the reflexive-transitive closure. 
To show antisymmetry note that $\lessdot_{\lPO} \subseteq \identOrd$
and $\lessdot_{\lRF} \subseteq \identOrd$ by construction. 
Therefore $\caOrd \subseteq \identOrd$. Since $\identOrd$ is
a partial order, it is antisymmetric, and thus $\caOrd$ should also be antisymmetric.
The axiom of finite cause, \ie $\prefix{e}$ is finite for every event $e$, 
follows from the fact that at each step of the construction 
the set of possible predecessors of the new event 
can be over-approximated by the finite sequence $\eventSeq$.

Second, we need to show that the conflict relation $\cfRel$ defined as 
described above obeys the laws of the conflict relation. 
Trivially, this relation is symmetric, and obeys the hereditary property.
The side condition $\neg (e_{\lPO} \cfRel e_{\lRF})$ of the rule \ESLoadRule
ensures that the conflict relation is irreflexive.

>>>>

First, we need to show that $\caOrd \ \defeq \ (\lPO \cup \lRF)^*$
is a partial order. Reflexivity and transitivity follows immediately 
from the definition of the reflexive-transitive closure. 
To show antisymmetry note that $\lessdot_{\lPO} \subseteq \identOrd$
and $\lessdot_{\lRF} \subseteq \identOrd$ by construction. 
Therefore $\caOrd$ is a subset of the reflexive closure of $\identOrd$. Since $\identOrd$ is
a partial order, it is antisymmetric, and thus $\caOrd$ should also be antisymmetric.
The axiom of finite cause, \ie $\prefix{e}$ is finite for every event $e$, 
follows from the fact that at each step of the construction 
the set of possible predecessors of the new event 
can be over-approximated by the finite sequence $\eventSeq$.

Second, we need to show that the conflict relation $\cfRel$ defined as 
described above obeys the laws of the conflict relation. 
Trivially, this relation is symmetric, and obeys the hereditary property.
The side condition $\neg (e \cfRel e_{\lRF})$ of the rule \ESLoadRule
ensures that the conflict relation is irreflexive.
